Prediction of Periprosthetic Joint Infection after Total Hip Arthroplasty: a simplified and externally validated model based on observational registry data from Sweden and Denmark

### 2020-12-14 diagnostics/README.Rmd

---
title: "External validation"
author: "Erik Bulow"
date: '`r Sys.Date()`'
output: 
  github_document:
    toc: yes
    df_print: "kable"
bibliography: 
  C:\\Users\\erik_\\Documents\\library.bib
---

>>>>

---
title: "External validation"
author: "Erik Bulow"
date: '`r Sys.Date()`'
output: 
#  github_document:
#    toc: yes
#    df_print: "kable"
  html_document:
    toc: yes
    df_print: "kable"
    toc_float: yes
    number_sections: yes
    code_folding: "hide"
    keep_md: yes
bibliography: 
  # C:\\Users\\erik_\\Documents\\library.bib
  H:\\zotero_lib.bib
---

### 2020-12-14 reports/article.Rmd

Logistic LASSO regression was performed for each sample using the chosen $\lambda_i$ as penalty term. Regression coefficients were ranked based on their absolute values as a measure of variable importance. We then used Bayesian methods to estimate a posterior distribution and to identify two change points in a linear segmented piecewise regression model. The second change point was then used as a break-point. Influential predictors with absolute coefficients value above this point, scored a point. The whole process, each with 100 Bootstrap replicates, was repeated 100 times (yielding 10,000 bootstrap samples in total). Potential predictors that were selected at least once out of 100 were then used in main effects multivariable logistic regression models without penalty and without pre-normalization of numeric variables. Even more parsimonious models with potential predictors chosen at least 50 out of 100 times were evaluated for comparison. Univariable prediction models based on either ASA class, the Charlson, Elixhauser, or the Rx Risk V comorbidity indices were fitted for comparison. Odds ratios for the final models were estimated with 95 % confidence intervals.

>>>>

Logistic LASSO regression was performed for each sample using the chosen $\lambda_i$ as penalty term. Regression coefficients were ranked based on their absolute values as a measure of variable importance. We then used Bayesian methods to estimate a posterior distribution and to identify two change points in a linear segmented piecewise regression model. The second change point was then used as a break-point. Influential predictors with absolute coefficients value above this point, scored a point. The whole process, each with 100 Bootstrap replicates, was repeated 100 times (yielding 10,000 bootstrap samples in total). Potential predictors that were selected at least `r brlasso_selection_n["main"]` out of 100 times were then used in main effects multivariable logistic regression models without penalty and without pre-normalization of numeric variables. Even more parsimonious models with potential predictors chosen at least `r brlasso_selection_n["reduced"]` out of 100 times were evaluated for comparison. Univariable prediction models based on either ASA class, the Charlson, Elixhauser, or the Rx Risk V comorbidity indices were fitted for comparison. Odds ratios for the final models were estimated with 95 % confidence intervals.
